Adolescent well-being in the digital age

### 2021-12-17 index.qmd
Colors

tmp %>% 
  ggplot(aes(i1_cb, val)) +
  scale_x_continuous(
    "Between-country centered internet adoption",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    fill = "dodgerblue2",
    alpha = .2
    ) +
  geom_line(aes(y = Estimate), col = "dodgerblue4") +
  geom_text(
    data = cb1_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

>>>>

tmp %>% 
  ggplot(aes(i1_cb, val)) +
  scale_x_continuous(
    "Between-country centered internet adoption",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, fill = "dodgerblue1"
    ) +
  geom_line(aes(y = Estimate), col = "dodgerblue4") +
  geom_text(
    data = cb1_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```
